Source-dependent likelihood-ratio ranking statistic for compact binary coalescence candidates

### 2016-09-28 article_rankstatsrc.tex
updated reference for chebyshev

The probabilities currently computed are a function of $\rho$: $P(\text{a signal is recovered by template }j|\rho)$. With a distribution of $\rho$, we can calculate:
	\begin{equation}
	P(\vec{t}_k|\text{signal}) = \int_{\rho_{\text{low}}}^{\rho_{\text{high}}} P(\vec{t}_k|\text{signal},\rho) P(\rho) d\rho
	\end{equation}

@@

>>>>

The probabilities currently computed are a function of $\rho$: $P(\text{a signal is recovered by template }j|\rho)$. The values of $\rho$ are chosen via Chebyshev nodes, as these are shown to reduce Runge's phenomenon when fitting \cite{numericalmethodsMATLAB}. The Chebyshev nodes in the interval (-1,1) are determined by the following:
	\begin{equation}
	x_k = \cos\Big(\frac{2k-1}{2n}\pi\Big), \quad k=1,...,n
	\end{equation}
where $n$ is a natural number.

With a distribution of $\rho$, we can calculate:
	\begin{equation}
	P(\vec{t}_k|\text{signal}) = \int_{\rho_{\text{low}}}^{\rho_{\text{high}}} P(\vec{t}_k|\text{signal},\rho) P(\rho) d\rho
	\end{equation}

@@

\begin{figure}
\includegraphics[width=0.5\textwidth]{logP_Ozelrho0_0.png}
\includegraphics[width=0.5\textwidth]{logP_Ozelrho16_3802850078.png}
\includegraphics[width=0.5\textwidth]{logP_Ozelrho51_2132034356.png}
\caption{$P(\vec{t}_k|\text{signal},\rho)$ for different values of $\rho$ for the BNS source population. The solid black lines denote the mass distribution of the respective source population model.}
\end{figure}
\begin{figure}
\includegraphics[width=0.5\textwidth]{logP_Kiziltanrho0_0.png}
\includegraphics[width=0.5\textwidth]{logP_Kiziltanrho16_3802850078.png}
\includegraphics[width=0.5\textwidth]{logP_Kiziltanrho51_2132034356.png}
\caption{$P(\vec{t}_k|\text{signal},\rho)$ for different values of $\rho$ for the BBH source population. The solid black lines denote the mass distribution of the respective source population model.}
\end{figure}

\begin{figure}
\includegraphics[width=0.5\textwidth]{lagrangian_fit_Ozel.pdf}
\includegraphics[width=0.5\textwidth]{lagrangian_fit_Kiziltan.pdf}
\label{fig:Pvsrho}
\caption{Lagrangian fits of $P_{jk}$ vs $\rho$ for a few templates (top: BNS, bottom: BBH). Dots are the data points, and solid lines are the functions found fitting Lagrangian polynomials to the data \FIXME{(change to cubic splines)}. The $\rho$ values are found using the Chebychev nodes, with the addition of $\rho=0$.}
\end{figure}
